%------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{calc}
\usepackage[normalem]{ulem} 

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheadingLeft}[2]{
    \item
    \begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
        \item[\small #1]{\textit{\small  #2}}
    \end{description}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
	\textbf{\Huge \scshape Ronak Jain} \\ \vspace{1pt}
	\small U.S. Citizen $|$ 617-840-1096 $|$ \href{mailto:ronak@ronakpjain.com}{\uline{ronak}} @ \href{https://ronakpjain.com}{\uline{ronakpjain.com}} $|$
	\href{https://github.com/ronakpjain}{\uline{github.com/ronakpjain}} $|$
	\href{https://www.linkedin.com/in/ronakpjain}{\uline{linkedin.com/in/ronakpjain}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Purdue University}{May 2028}
{B.S. in Electrical Engineering, GPA: 3.47/4.0}{West Lafayette, IN}
\resumeSubSubheadingLeft
{Relevant Coursework:}{Data Structures and Algorithms, Operating Systems, Microprocessor Systems and Interfacing, ASIC Design Lab,  Signals and Systems, Probabilistic Methods, Digital System Design}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://github.com/PurdueElectricRacing/firmware}{\uline{Purdue Electric Racing}}}{September 2024 -- Present}
\resumeItemListStart
\resumeItem{Engineered FDCAN message routing and filtering library with support for standard and extended identifiers, facilitating reliable inter-controller communication across the vehicle.}
\resumeItem{Developed comprehensive USART and SPI hardware abstraction layers with DMA support for efficient multi-protocol sensor data acquisition and vehicle integration.}
\resumeItem{Implemented G4 HSE clock driver enabling 16MHz external oscillator synchronization with PLL support up to 168MHz for deterministic real-time control.}
\resumeItem{Migrated bare-metal task scheduler to FreeRTOS, improving real-time determinism for safety-critical functions.}
\resumeItem{Designed CI/CD pipeline automating firmware builds, artifact packaging, and release management.}
\resumeItem{Contributed to DaqApp2 Rust application enabling real-time CAN message visualization for vehicle analysis.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/PurdueRM/Embedded-Control}{\uline{Purdue Robomasters}} -- Controls Subteam Lead}{August 2024 -- January 2026}
\resumeItemListStart
\resumeItem{Lead the controls subteam in developing high-performance firmware for STM32 microcontrollers using C, overseeing the complete software development lifecycle for robotic systems.}
\resumeItem{Carried out a refactor of the legacy codebase, establishing a modular interface to streamline the integration of a new, more powerful STM32H7 series microcontroller.}
\resumeItem{Architected and implemented advanced control algorithms, including PID and odometry, for omni-wheel and swerve-drive robots to achieve precise and fluid battlefield maneuverability.}
\resumeItem{Implemented and debugged firmware on-site during the annual Robomaster competition, adapting control logic in a high-pressure environment to meet changing strategic needs.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/ronakpjain/ronfire}{\uline{Ronfire}}}{May 2025 -- Present}
\resumeItemListStart
\resumeItem{Engineered a high-performance, asynchronous HTTP server in Rust using Tokio, optimizing the non-blocking I/O architecture to achieve a sustained throughput of over 4,100 requests/sec (1.65 GB/s) when serving image files over Unix domain sockets.}
\resumeItem{Implemented concurrent request processing and multiplexing to handle multiple simultaneous client connections, maximizing server throughput and enabling efficient resource utilization in high-concurrency environments.}
\resumeItem{Developed a robust HTTP request parsing engine with full GET request support, including Content-Type negotiation through MIME-type guessing and comprehensive error handling for protocol compliance.}
\resumeItem{Integrated path traversal sanitization and validation mechanisms to ensure secure file serving, preventing directory escape attacks while maintaining backward compatibility with standard HTTP semantics.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/ronakpjain/ronq}{\uline{Ronq}}}{June 2025 -- Present}
\resumeItemListStart
\resumeItem{Designed and implemented a modern C++ command runner utility leveraging C++20 features to execute multiple shell commands in parallel with full process management and RAII principles.}
\resumeItem{Architected a safe file descriptor wrapper using move semantics and exclusive ownership patterns, eliminating resource leaks and ensuring deterministic cleanup of system resources across process boundaries.}
\resumeItem{Developed an error handling system using \texttt{std::expected} for zero-overhead exception-free error propagation, providing compile-time type safety for command execution failures.}
\resumeItem{Implemented a colored output system that dynamically assigns ANSI color codes to concurrent commands, improving terminal readability and making parallel execution monitoring more intuitive.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/ronakpjain/dots}{\uline{Dots}}}{September 2024 -- Present}
\resumeItemListStart
\resumeItem{Built a highly customized MacOS and Linux setup enhancing developer productivity with integrated debugging (DAPs), comprehensive language server support (LSPs), and streamlined workflows}
\resumeItemListEnd

\resumeSubHeadingListEnd

% %-----------EXPERIENCE-----------
% \section{Experience}
% \resumeSubHeadingListStart
%
% \resumeSubheading
% {Mentor}{December 2022 -- August 2024}
% {Einstein's Workshop}{Burlington, MA}
% \resumeItemListStart
% \resumeItem{Instructed and mentored students in computer science and engineering subjects, including programming and CAD, fostering hands-on learning and creativity}
% \resumeItem{Organized summer camps with over 20 students each week, delivering sessions on Minecraft Modding and 3D Printing, cultivating critical thinking and technical skills in an engaging environment}
% \resumeItem{Coordinated and managed up to 3 birthday parties per weekend, overseeing projects, event logistics, and ensuring a fun and welcoming environment for attendees}
% \resumeItemListEnd
%
% \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Languages}{: C, C++, Rust, Python, Lua} \\
	      \textbf{Developer Tools}{: Git, Docker, \textbf{NeoVim}} \\
	      }}
\end{itemize}

%-------------------------------------------
\end{document}
